Hybrid platforms and bargaining power

### 2023-02-03 src/paper/application.tex
Add equilibrium subsection

@@

I make use of a reduced-form, but quite general approach to model production and demand.
Assume that the total profits obtained by the platform and the fringe sellers are described by the function $f(n_P, n_F)$.
Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
In case the platform operates as a pure intermediary, $n_P = 0$.
For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.

@@

\subsection{Equilibrium}

\begin{assumption}
    \label{ass:single_crossing}
    Let $f(n_P, n_F)$ and $w(s)$ be such that the following holds for all $N_F, N_P \geq 0$:
    \begin{gather*}
        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
        \text{or} \\
        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
    \end{gather*}
\end{assumption}

\section{Example}
\label{sec:model}

>>>>

Assume that there are two types of players in the market: a platform $P$ and a continuum of fringe sellers $F_i$.

@@

I make use of a reduced-form, but quite general approach to model production and demand.
First, I assume that all fringe firms are ex-ante identical.
This implies that the total profits of the platform and the fringe taken together have a simple functional form $f(n_P, n_F)$.
\begin{assumption}
    \label{ass:identical_fringe}
    The total profits of the platform and the fringe are described by some function $f: \mathbb{R}^+_0 \times \mathbb{R}^+_0 \to \mathbb{R}^+_0$.
\end{assumption}
Here, $n_F$ is the mass of fringe sellers, and $n_P$ measures the degree to which the platform sells its own products.
For example, in a setting with differentiated products and monopolistic competition, $n_F$ and $n_P$ represents the product variety of the fringe and the platform, respectively.
In case the platform operates as a pure intermediary, $n_P = 0$.

@@

Let us now turn to the determination of the equilibrium number of fringe firms.
Assume that there is an unlimited number of potential fringe entrants, indexed by $i \in \mathbb{R}^+_0$.
In the first stage of the game, each fringe firm must create a viable product at the investment cost $I_F > 0$.
In the second stage, firms that made this investment plus the platform engage in producing and selling their respective products.
If there are $N_F$ fringe entrants and $N_P$ platform products, then, as discussed previously, the total profit they make together is given by $f(N_P, N_F)$.
Finally, the platform and the entrants share this profit according to the profit sharing rule from \cref{ass:profit_sharing}.

The equilibrium number of entrants is determined by a free entry condition: in the end, the fringe firms' profits should be equal to the investment cost.
\begin{assumption}
    \label{ass:free_entry}
    In equilibrium, $\pi_F(N_P, N_F) = I_F N_F$.
\end{assumption}

In order to guarantee a unique equilibrium, let us make the following, additional assumption about the profit and bargaining weight functions.
\begin{assumption}
    \label{ass:single_crossing}
    Let $f$ and $w$ be such that the following holds for all $N_F, N_P \geq 0$:
    \begin{gather*}
        f'_{n_F} (N_P, N_F) < \int_0^1 s w(s) f'_{n_F} (N_P, s N_F) \ds \\
        \text{or} \\
        f''_{n_F} (N_P, N_F) < \int_0^1 s^2 w(s) f''_{n_F} (N_P, s N_F) \ds.
    \end{gather*}
\end{assumption}
\textcolor{red}{TODO: Find interpretable sufficient conditions for this assumption.}

\section{Results}

\begin{proposition}

\end{proposition}

\section{Example}
\label{sec:example}
